# Data sources

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE)
```

```{r, echo=FALSE}
library(tidyverse)
library(readr)
```

## URL of data sources
Our data are collected from a website of IMDB (https://datasets.imdbws.com/). Collecting the datasets is pretty straightforward. We just downloaded the `tsv.gz` files we need. These files are `title.ratings.tsv.gz`, `name.basics.tsv.gz`, `title.basics.tsv.gz`, `title.crew.tsv.gz`, and `title.principals.tsv.gz`.

## Basic information
```{r, echo=FALSE, eval=FALSE}
title.ratings <- read_tsv("data/title.ratings.tsv.gz")
name.basics <- read_tsv("data/name.basics.tsv.gz") # 
title.basics <- read_tsv("data/title.basics.tsv.gz") 
title.crew <- read_tsv("data/title.crew.tsv.gz")
title.principals <- read_tsv("data/title.principals.tsv.gz")
```

```{r, echo=FALSE}
load('data/title.basics.RData')
load('data/name.basics.RData')
load('data/title.crew.RData')
load('data/title.ratings.RData')
load('data/title.genres.RData')
```


### title.basics

Here are the first few rows of the dataframe of `title.basics`. 
```{r}
head(title.basics)
```

`title.basics` contains some basic information for movie or tv show titles.

tconst (chr) - alphanumeric unique identifier of the title

titleType (chr) – the type/format of the title (e.g. movie, short, tvseries, tvepisode, video, etc)

primaryTitle (chr) – the more popular title / the title used by the filmmakers on promotional materials at the point of release

originalTitle (chr) - original title, in the original language

isAdult (dbl) - 0: non-adult title; 1: adult title

startYear (chr) – represents the release year of a title. In the case of TV Series, it is the series start year

endYear (chr) – TV Series end year. ‘\N’ for all other title types

runtimeMinutes (chr) – primary runtime of the title, in minutes

genres (chr) – includes up to three genres associated with the title

The number of rows in the dataframe of `title.basics` is: 

```{r}
nrow(title.basics)
```

### name.basics

Here are the first few rows of the dataframe of `title.basics`. 
```{r}
head(name.basics)
```

`name.basics` contains some basic information of people.

nconst (chr) - alphanumeric unique identifier of the name/person

primaryName (chr) – name by which the person is most often credited

birthYear (chr) – birth year

deathYear (chr) – death year

primaryProfession (chr) – the top-3 professions of the person

knownForTitles (chr) – titles the person is known for

The number of rows in the dataframe of `name.basics` is: 

```{r}
nrow(name.basics)
```

### title.ratings

Here are the first few rows of the dataframe of `title.ratings`. 
```{r}
head(title.ratings)
```

`title.ratings` contains the IMDb rating and votes information for titles.

tconst (chr) - alphanumeric unique identifier of the title 

averageRating (dbl) – weighted average of all the individual user ratings

numVotes (dbl) - number of votes the title has received

The number of rows in the dataframe of `title.ratings` is: 

```{r}
nrow(title.ratings)
```
### title.crew

Here are the first few rows of the dataframe of `title.crew`. 
```{r}
head(title.crew)
```

`title.crew` contains the director and writer information for all the titles in IMDb.

tconst (chr) - alphanumeric unique identifier of the title

directors (chr) - director(s) of the given title

writers (chr) – writer(s) of the given title

The number of rows in the dataframe of `title.crew` is: 

```{r}
nrow(title.crew)
```
### title.principals

Here are the first few rows of the dataframe of `title.principals`. 
```{r}
head(title.principals)
```

`title.principals` contains the principal cast/crew for titles.

tconst (chr) - alphanumeric unique identifier of the title

ordering (chr) – a number to uniquely identify rows for a given titleId

nconst (chr) - alphanumeric unique identifier of the name/person

category (chr) - the category of job that person was in

job (chr) - the specific job title if applicable, else '\N'

characters (chr) - the name of the character played if applicable, else '\N'

The number of rows in the dataframe of `title.principals` is: 

```{r}
nrow(title.principals)
```

## Issues

There are some issues with the datasets. First, the data types of some columns are wrong. For example, `runtimeMinutes` should be integers rather than strings. Second, the missing values are represented with "\\\\N". In the next section, we will transform the datasets so that they have correct data types and NA as missing values.

