# Missing values

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE)
```

## Repuired libraries

```{r}
library(tidyverse)
library(readr)
```

## Load and show the initial data
```{r}
basic <- read_tsv("data/name.basics.tsv.gz")
head(basic)
```

From the output table, we can see that the missing values in this dataset are represented with "\\\\N". Next, we are going to replace "\\\\N" with NA.

## Replace "\\\\N" with NA
```{r}
basic$nconst <- gsub("\\N", NA, basic$nconst, fix=TRUE)
basic$primaryName <- gsub("\\N", NA, basic$primaryName, fix=TRUE)
basic$birthYear <- gsub("\\N", NA, basic$birthYear, fix=TRUE)
basic$deathYear<- gsub("\\N", NA,basic$deathYear, fix=TRUE)
basic$primaryProfession <- gsub("\\N", NA, basic$primaryProfession, fix=TRUE)
basic$knownForTitles <- gsub("\\N", NA, basic$knownForTitles, fix=TRUE)
```

## Show the data after transformation
```{r}
head(basic)
```


## Missing patterns

### Missing values by column
```{r}
colSums(is.na(basic)) %>%
  sort(decreasing = TRUE)
```


### Show the missing patterns 
```{r}
source("scripts/visna.R")
visna(basic)
visna(basic, percent=TRUE)
```

From the graph, we can see that there are no missing values in columns `nconst` and `primaryName`. Most missing values are in columns `deathYear` and `birthYear`. This might be due to the difficulty of getting the specific birth and death time and the fact that some people are not dead. Only a minority of missing values are in columns `primaryProfession` and `knownForTitles`. Furthermore, `deathYear` and `birthYear` are both missing in most rows with missing data. It might be due to the high correlation between these 2 columns. Only a very small proportion of rows have no missing values. 
